Demo: Programming Distributed Control Planes

### 2017-03-13 paper/propane/SOSR/sosr.tex
more edits to section 7
add copyright info to SOSR submission

\conferenceinfo{SOSR'17,}{April 3--4, 2017, Santa Clara, CA.} 
\copyrightetc{\copyright~2017 ACM. ISBN \the\acmcopyr}
\crdata{xxx.\\
DOI: http://dx.doi.org/10.1145/XXX.XXXXXXX}
% Update the XXX's to the DOI assigned by ACM rightsreview forms
\clubpenalty=10000 
\widowpenalty = 10000

@@

@@

%=====================================================
%
%
%  **Keywords**
%
%
%=====================================================

@@

\keywords{Propane; Domain-specific Language; BGP; Compilation; Fault Tolerance; Distributed Systems}

>>>>

%\conferenceinfo{SOSR'17,}{April 3--4, 2017, Santa Clara, CA.} 
%\copyrightetc{\copyright~2017 ACM. ISBN \the\acmcopyr}
%\crdata{xxx.\\
%DOI: http://dx.doi.org/10.1145/XXX.XXXXXXX}
%% Update the XXX's to the DOI assigned by ACM rightsreview forms
%\clubpenalty=10000 
%\widowpenalty = 10000

@@

\CopyrightYear{2017} 
\setcopyright{acmlicensed}
\conferenceinfo{SOSR '17,}{April 03 - 04, 2017, Santa Clara, CA, USA}
\isbn{978-1-4503-4947-5/17/04}\acmPrice{\$15.00}
\doi{http://dx.doi.org/10.1145/3050220.3063774}

@@

%=====================================================
%
%
%  **Keywords and Descriptions**
%
%
%=====================================================

@@

\keywords{Propane; Domain-specific Language; BGP; Fault Tolerance; Compilation, SDN, Network Control Plane}
